Measuring security performance in the Android ecosystem

### 2015-06-03 security_scoring.tex
Bring security scoring up one level to be a section

\subsection{Comparing device manufacturers, device models and network operators}
\label{sec:security_scoring}\label{sec:exp:security_score}

@@

\subsubsection{Method: Scoring for security}

@@

\subsubsection{Results: Security scores}\label{sec:security_scoring:results}
The scores across the whole of Android are that \daMeanInsecurityPerc\ of devices are exposed to known root exploits.
There are on average \daMeanOutstandingVulnerabilities\ outstanding vulnerabilities not fixed on any device.
Only on average \daUpdatednessPerc\ of devices run the most recent version of Android.
This gives a security score of \daSecurityScore\ out of 10.
\daTabSecScoressummary
However there are a wide variety of scores depending on the source of the device.
There have been many reports\todolater{citation} that Google's Nexus devices are better at getting updates than other Android devices because Google makes the original updates and ships them to its devices.
Table~\ref{tab:sec_summary} shows that this is the case with Nexus devices getting much better scores than non-Nexus devices.
\daTabSecScoresmanufacturer
Different device manufacturers have very different scores, Table~\ref{tab:sec_manufacturer} shows the scores for the \daNumSigManufacturers\ device manufacturers with a significant presence in our data with \emph{\daSecScoreBestmanufacturer} (\daSecScoreBestmanufacturerScore\ out of 10) scoring highest and \emph{\daSecScoreWorstmanufacturer} (\daSecScoreWorstmanufacturerScore\ out of 10) scoring lowest.
Device manufacturers are considered significant if we have data from at least \daSigNumDevices\ devices and at least \daSigNumDeviceDays\ days of contributions.
Additionally for $m$ and $u$ we ignore days with less than \daSigNumDevicesDay\ devices contributing to that day's score.

@@

\subsubsection{Sensitivity of scoring metric}
\daTabDLDistances
\daTabChangeInScores
To evaluate whether the ranking of different manufacturers is sensitive to the form of the scoring metric we computed the normalised Damerau-Levenshtein distance~\cite{Bard2007} between the lists ordered using different forms of the scoring metric, this is shown in Table~\ref{tab:dl_distances}.
The `equal' metric weights $f$, $u$ and $m$ equally rather than favouring $f$ and makes little difference.
Changing the scoring metric also impacts the scores given for each entity Table~\ref{tab:change_in_scores} shows the mean impact on the scores.
\todo{Give some of the actual orderings as well for the most important ones}

\subsubsection{Scores over time}
\begin{figure}
\centering
\includegraphics[width=\columnwidth]{figures/security_score_manufacturer}
\caption{Security scores for different manufacturers}
\label{fig:security_score_manufacturer}
\includegraphics[width=\columnwidth]{figures/security_score_model}
\caption{Security scores for different device models}
\label{fig:security_score_model}
\includegraphics[width=\columnwidth]{figures/security_score_operator}
\caption{Security scores for different operators}
\label{fig:security_score_operator}
\includegraphics[width=\columnwidth]{figures/security_score_summary}
\caption{Security scores for Nexus and non-Nexus devices}
\label{fig:security_score_summary}
\end{figure}
The scoring metric as originally computed is averaged over the whole history of the device manufacturer, device model or network operator, it gives equal weight to periods years ago as to in the last few months.
If instead we take an exponential moving average of the daily score for days with more than \daSigNumDevicesDay\ devices when there have been at least consecutive \daSigNumDays\ days of data with that many devices with an $\alpha$ of $1/\daSigNumDays$ then we can plot how this score has changed over time.
Equation~\ref{eq:rolling_update} shows how the value for a particular day ($v_i$) is computed from the previous day's value and the input for the current day ($n$).
\begin{equation}
v_i = v_{i-1} (1 - \alpha) + n \alpha
\label{eq:rolling_update}
\end{equation}
Figure~\ref{fig:security_score_manufacturer} shows this for manufacturers, Figure~\ref{fig:security_score_model} for device models, Figure~\ref{fig:security_score_operator} for operators Figure~\ref{fig:security_score_summary} for Nexus and non-Nexus devices.
These show how the scores for different entities are different and change over time, while there is correlated behaviour for different entities (due to things like new vulnerabilities affecting all Android being discovered) these lines still have crossings due to the different behaviour of the different entities.
It also shows that we do not have sufficient data for all the entities all of the time, resulting in gaps in the data.
The clearest results are for Figure~\ref{fig:security_score_summary} with a large gap between the scores for Nexus and non-Nexus devices across the whole data set.

>>>>

\section{Comparing device manufacturers, device models and network operators}
\label{sec:security_scoring}\label{sec:exp:security_score}

@@

\subsection{Method: Scoring for security}\label{sec:security_scoring:method}

@@

\subsection{Results: Security scores}\label{sec:security_scoring:results}
The scores across the whole of Android are that \daMeanInsecurityPerc\ of devices are exposed to known root exploits.
There are on average \daMeanOutstandingVulnerabilities\ outstanding vulnerabilities not fixed on any device.
Only on average \daUpdatednessPerc\ of devices run the most recent version of Android.
This gives a security score of \daSecurityScore\ out of 10.
\daTabSecScoressummary
However there are a wide variety of scores depending on the source of the device.
There have been many reports\todolater{citation} that Google's Nexus devices are better at getting updates than other Android devices because Google makes the original updates and ships them to its devices.
Table~\ref{tab:sec_summary} shows that this is the case with Nexus devices getting much better scores than non-Nexus devices.
\daTabSecScoresmanufacturer
Different device manufacturers have very different scores, Table~\ref{tab:sec_manufacturer} shows the scores for the \daNumSigManufacturers\ device manufacturers with a significant presence in our data with \emph{\daSecScoreBestmanufacturer} (\daSecScoreBestmanufacturerScore\ out of 10) scoring highest and \emph{\daSecScoreWorstmanufacturer} (\daSecScoreWorstmanufacturerScore\ out of 10) scoring lowest.
Device manufacturers are considered significant if we have data from at least \daSigNumDevices\ devices and at least \daSigNumDeviceDays\ days of contributions.
Additionally for $m$ and $u$ we ignore days with less than \daSigNumDevicesDay\ devices contributing to that day's score.

@@

\subsection{Scores over time}
\begin{figure}
\centering
\includegraphics[width=\columnwidth]{figures/security_score_manufacturer}
\caption{Security scores for different manufacturers}
\label{fig:security_score_manufacturer}
\includegraphics[width=\columnwidth]{figures/security_score_model}
\caption{Security scores for different device models}
\label{fig:security_score_model}
\includegraphics[width=\columnwidth]{figures/security_score_operator}
\caption{Security scores for different operators}
\label{fig:security_score_operator}
\includegraphics[width=\columnwidth]{figures/security_score_summary}
\caption{Security scores for Nexus and non-Nexus devices}
\label{fig:security_score_summary}
\end{figure}
The scoring metric as originally computed is averaged over the whole history of the device manufacturer, device model or network operator, it gives equal weight to periods years ago as to in the last few months.
If instead we take an exponential moving average of the daily score for days with more than \daSigNumDevicesDay\ devices when there have been at least consecutive \daSigNumDays\ days of data with that many devices with an $\alpha$ of $1/\daSigNumDays$ then we can plot how this score has changed over time.
Equation~\ref{eq:rolling_update} shows how the value for a particular day ($v_i$) is computed from the previous day's value and the input for the current day ($n$).
\begin{equation}
v_i = v_{i-1} (1 - \alpha) + n \alpha
\label{eq:rolling_update}
\end{equation}
Figure~\ref{fig:security_score_manufacturer} shows this for manufacturers, Figure~\ref{fig:security_score_model} for device models, Figure~\ref{fig:security_score_operator} for operators Figure~\ref{fig:security_score_summary} for Nexus and non-Nexus devices.
These show how the scores for different entities are different and change over time, while there is correlated behaviour for different entities (due to things like new vulnerabilities affecting all Android being discovered) these lines still have crossings due to the different behaviour of the different entities.
It also shows that we do not have sufficient data for all the entities all of the time, resulting in gaps in the data.
The clearest results are for Figure~\ref{fig:security_score_summary} with a large gap between the scores for Nexus and non-Nexus devices across the whole data set.

\subsection{Sensitivity of scoring metric}
\daTabDLDistances
\daTabChangeInScores
To evaluate whether the ranking of different manufacturers is sensitive to the form of the scoring metric we computed the normalised Damerau-Levenshtein distance~\cite{Bard2007} between the lists ordered using different forms of the scoring metric, this is shown in Table~\ref{tab:dl_distances}.
The `equal' metric weights $f$, $u$ and $m$ equally rather than favouring $f$ and makes little difference.
Changing the scoring metric also impacts the scores given for each entity Table~\ref{tab:change_in_scores} shows the mean impact on the scores.
\todo{Showing?}
\todo{Give some of the actual orderings as well for the most important ones}
\todo{Sensitivity of time based vs. global scores}
